### 2021-12-08 text/outline/draft.tex
add Fig 5a

We compared GLM-EIV to thresholded regression on the real data, focusing specifically on the negative control pairs (i.e., gene-perturbation pairs that, by design, are expected to exhibit a fold change of $1$, or no association). We found that GLM-EIV and the thresholding method produced similar results (Figure \ref{fig:real_data}a-b): estimates, CI coverage rates, and CI widths were concordant. We note that GLM-EIV produced outlier estimates (likely due to non-global EM convergence) on a small ($< 2\%$ on Gasperini, $<0.05\%$ on Xie) number of pairs consisting of a handful of genes (not plotted). The estimated effect of the perturbation on gene expression $\exp(\hat{\beta}_1^g)$ was unexpectedly large (95\% CI $[XX,XX]$ and $[300,316]$ on Gasperini and Xie data, respectively). We concluded that the datasets lay in an ``easy'' region of the parameter space, making thresholding a tenable strategy (provided the threshold is selected well).

>>>>

We compared GLM-EIV to thresholded regression on the real data, focusing specifically on the negative control pairs (i.e., gene-perturbation pairs that, by design, are expected to exhibit a fold change of $1$, or no association). We found that GLM-EIV and the thresholding method produced similar results (Figure \ref{fig:real_data}a-b): estimates, CI coverage rates, and CI widths were concordant. We note that GLM-EIV produced outlier estimates (likely due to non-global EM convergence) on a small ($< 2.5 \%$ on Gasperini, $<0.05\%$ on Xie) number of pairs consisting of a handful of genes (not plotted). The estimated effect of the perturbation on gene expression $\exp(\hat{\beta}_1^g)$ was unexpectedly large (95\% CI $[4306, 5186]$ and $[300, 316]$ on Gasperini and Xie data, respectively). We concluded that the datasets lay in an ``easy'' region of the parameter space, making thresholding a tenable strategy (provided the threshold is selected well).
